---
title: "Linear Regression"
author: "Imad Dabbura"
data: "10/31/2017"
output:
    #pdf_document: default
    html_document: default
---

```{r, echo=FALSE, message=FALSE}
library(ISLR)
library(corrplot)
library(ggplot2)
library(psych)
library(car)
```
## Introduction

**Income:** Income in $10,000's.

**Limit:** Credit limit.

**Rating:** Credit rating.

**Cards:** Number of credit cards.

**Age:** Age in years.

**Education:** Number of years of education.

**Gender:** A factor with levels Male and Female.

**Student:** A factor with levels No and Yes indicating whether the individual was a student.

**Married:** A factor with levels No and Yes indicating whether the individual was married.

**Ethnicity:** A factor with levels African American, Asian, and Caucasian indicating the individual's ethnicity.

**Balance:** Average credit card balance in $.

```{r, echo=FALSE}
Credit <- Credit[, -1]
str(Credit)
```



```{r, echo=FALSE}
corrplot(cor(Credit[, -c(8:11)]), addCoef.col = "grey", type = "lower",
         tl.srt = 45, tl.cex = 0.9)
mtext("Correlation Plot", outer = TRUE, cex = 1.2)
```

```{r, echo=FALSE}
pairs.panels(Credit[, -c(1, 8:11)])
```


```{r}
hist(log(Credit$Balance), breaks = 15)
hist(Credit$Balance, breaks = 15)
hist(sqrt(Credit$Balance), breaks = 15)
```

```{r}
reg_fit <- lm(Balance ~ . + Limit:Rating, data = Credit)
summary(reg_fit)
```


```{r}
vif(reg_fit)
```

